Viscous Transport in Eroding Porous Media

### 2019-05-06 docs/transport/erosion_transport.tex
doing in tranposrt paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barcyentric Quadrature for $v''(x)$}
In order to simulate erosion, we require the deformation gradient which
means that a quadrature rule for $v''(x)$ is required.  Using the same
techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
quadrature rule for the second derivative can be constructed using the
identities
{\color{red}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.

@@

{\color{red}
To numerically approach the nearly singular integraton by using Barycentric quadrature rule,

To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
}
\begin{itemize}
  \item Apply trapezoid rule as a first pass

@@

}
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly

{\color{red} \item Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency

To find the suitable values of $\alpha_1$ and $\alpha_2$ in~\eqref{eqn:Cw2b} and \eqref{eqn:Cb2b}, we set $\alpha_1=\alpha_2=1, 2, 3$, and $4$ to test the criteria on a 20-body problem with $N_\out = 1024$ and $N_\iin = 128, 256$, and $512$. To check the accuracy of the simulations, we use (?)
To see how efficient our code is, we record the cpu time for each step.

}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
{\color{red} We first consider a circular body in a shear flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow form the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the initial minimum distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
In order to simulate erosion, we require the deformation gradient which
means that a quadrature rule for $v''(x)$ is required.  Using the same
techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
quadrature rule for the second derivative can be constructed using the
identities
{\color{red}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.

@@

{\color{red}
By using Barycentric quadrature rule to approach integrations, we get a reasonable(?) double-layer potential and quantities of interest at target points but it requires $\mathcal{O}(N^2)$ operations per target point which is computational expensive if we impose it on all the target points. In order to accelerate the process and keep the accuracy, it is a compromise that we use Barycentric quadrature rule to approach the nearly singular integratons but apply trapezoid rule when the target point is far from source points.

To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points. The following is the four-step fast summation methods.
}
\begin{itemize}
  \item Apply trapezoid rule as a first pass

@@

}
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly
\end{itemize}
{\color{red}  (Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency)

To find the suitable values of $\alpha_1$ and $\alpha_2$ in~\eqref{eqn:Cw2b} and \eqref{eqn:Cb2b}, we set $\alpha_1=\alpha_2=1, 2, 3$, and $4$ to test the criteria on a 20-body problem with $N_\out = 1024$ and $N_\iin = 128, 256$, and $512$. To check the accuracy of the simulations, we use the solution calculated by \todo[inline]{what method} to \todo[inline]{...}
To see how efficient our code is, we record the cpu time for each step.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the local shear stress on the body. In this simulation, we use three the minimum body-to-wall initial distance $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
\label{01bodseq} 
\end{center}
\end{figure}
{\color{red} We first consider a circular body in a shear flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow form the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. Let the radius of the body be $r$, the length of the body be $L$, $N_\iin$ and $N_\out$ be the number of discretization points on the body and wall respectively, $h=L/N_\iin$ be the resolution mesh size of the body, and $d$ be the minimum initial distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ with respect to three different $d=h, h/2$, and $ h/10$.
